One-dimensional turbulence (ODT): computationally efficient modeling and simulation of turbulent flows

### 2020-05-30 manuscript/manuscript.tex
Drafting text of workflow section. Unfinished.

@@

@@

%\subsection{General Workflow}
%\label{sub:workflow}
%
%Every ODT simulation shares common steps to a successful run. 
%\begin{enumerate}
%	\item Build and compile the code. 
%	\item Choose a case type and chemical mechanism (when required) and alter the appropriate input file(s). 
%	\item Within the \texttt{run} directory, alter the run script to be used with a case name and other required information.
%	\item Run the case from the \texttt{run} directory using the chosen run script.
%	\item Run the appropriate post-processing scripts, located in the \texttt{post} directory, on the raw data for interpretation and visualization.
%\end{enumerate}

\subsection{Pipe Flow}
\label{sub:pipeflow}

>>>>

This section outlines the process a user would go through in order to successfully build the ODT code and run a simulation. For more details, please see the package documentation. ODT is a standalone, self-contained package, and users interact with its files primarily via the command line rather than a graphical interface.

@@

\subsubsection{Building ODT}

The ODT build process is relatively automated through CMake. First, navigate to the \texttt{build} directory and edit the CMake configuration file. Note that the user must specify which chemical mechanism to compile with before building the code. In order to run simulations with different chemical mechanisms, the code must be recompiled, including the CMake configuration files, between simulations, whereas this is not required when other variables are changed. This is a known inconsistency that will be changed in future code releases. The CMake configuration file also specifies Cantera's location and must be changed to reflect the local installation location. Once the settings are correct, the user runs CMake to apply these changes.

YAML is required in order to process input files. If it has not yet been installed, it is built and installed at this point. For convenience, the ODT package includes the appropriate files and automates this process. YAML need only be installed once for a given instance of the ODT package. Rebuilding the ODT code with CMake does not affect the YAML installation.

Once CMake and YAML have been prepared, the user can build the ODT code with the appropriate \texttt{make} command. There is no associated \texttt{install} command that needs to be run. The most common errors that occur during the build process concern incorrect file paths or incomplete installation of precursor packages. See the build documentation for troubleshooting help.

Once the code is built, the user may optionally build a local copy of the documentation via Doxygen, which must be previously installed. This step is not required in order to run the ODT code. As an alternative, documentation can be accessed via \texttt{README} files within the code or at the code repository wiki.

\subsubsection{Input files}

User-modified input files are located within the \texttt{input} directory, which contains subdirectories that correspond to various case types that can be run with ODT. At minimum, a case's subdirectory contains an \texttt{input.yaml} file, but may contain other files or subfolders. ODT has the capability to restart a simulation from a specified time or state. To use this function, a raw data file at the required state must be copied to the input case directory and renamed \texttt{restart.dat}. For an example, please see the \texttt{jetFlame/flameD} case. Note that the user must also change the \texttt{Lrestart} parameter within the \texttt{input.yaml} file in order to use the restart feature. Input case directories may also contain subdirectories with supplemental information or input file examples; only the \texttt{input.yaml} file located in the base case input directory is used in a simulation.

The \texttt{input} directory also contains the \texttt{gas\textunderscore mechanisms} subdirectory, which contains chemical mechanism files in XML format that can be used in reacting flow cases. For cases in which a chemical mechanism is not required, the \texttt{not\textunderscore used.xml} mechanism file is specified in the appropriate \texttt{input.yaml} file in place of other mechanisms. Note that the chemical mechanism chosen for the case and specified in the input file must match the mechanism specified in the Cmake configuration file during the ODT build process.

Input files contain simulation parameters in a human-readable format parsed by YAML. Not all of the parameters in an input file may be used in a given simulation. An overview of possible ODT parameters will be covered here, but does not represent all the possibilities or functions of ODT; please see the associated documentation for more information. Input files are divided into sections, several of which are common to all \texttt{input.yaml} files; these are summarized in Table \ref{tab:input_sections}. Details about individual parameters, including usage and typical values, are covered in the documentation.

\begin{table}
\begin{tabular}{|l|p{4.1in}|}
\hline
Section 				& Description 	\\
\hline
\texttt{params}* 		& General parameters, including simulation length, domain size, and ODT parameters ($C$, $Z$, $\beta_{LES}$) \\
\texttt{radParams}		& Radiation parameters; only relevant to reacting flow cases (i.e. jet flames) \\
\texttt{streamProps}	& Stream properties; used when there are two or more separate streams (i.e. non-premixed jets)\\
\texttt{bcCond}* 		& Boundary conditions for velocity and temperature (where required) \\
\texttt{initParams} 	& Case-specific initialization parameters, usually flow geometry and stream velocities \\
\texttt{dumpTimes}*		& List of simulation time steps at which to output data files \\
\hline
\end{tabular}
\caption{Common sections present in \texttt{input.yaml} files. Sections marked with a * should be present in every \texttt{input.yaml} file regardless of case type. Sections usually appear in this order, but this is not required.}
\label{tab:input_sections}
\end{table}

Prior to running a simulation, the user must select and modify the appropriate \texttt{input.yaml} file to reflect the desired conditions. The default values already present in the input files represent general parameters that may be used to run a successful simulation of that case type.

\subsubsection{Running ODT}

@@

%-----------------------------------------------------------------------------------
\subsection{Pipe Flow}
\label{sub:pipeflow}
